A survey of HTTP caching options on the open Web

### 2015-01-14 sanity/paper1.tex
Conclusions
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@982 43ef1190-90fd-4dd7-a769-d0121f02b80e

While these studies have little overlap with the present paper, they
underline the importance of understanding the current deployment and
future potential. In some of the related work, it is shown that
caching does not necessarily give tanglible benefits. Yet, we shall
assume that sharing the metadata required for caching outside of the
server is desireable, and that it is possible in most cases. We shall
see that it most likely will be beneficial in cases that do not
benefit from caching today.

@@

The two most important headers to control caching are \httph{Expires}
and \httph{Cache-Control}. As shown in Table~\ref{tab:headers}, there
are also others. We found \httph{Pragma} in 287 responses, but except
for two hosts, where they were superflous, they were only used to
prohibit caching. \httph{Surrogates} were not observed.

@@

Of these resources, 405 returned valid headers, but 114 did so to
\emph{prohibit} caching of the response, and 3 contained conflicting
headers, i.e. set an freshness lifetime, but also prohibited
caching. In most cases, \httph{Cache-Control} and \httph{Expires} both
occured, but the former is more common than the latter in the cases
where only one of them occur.  Additionally, 269 resources had a
\httph{Cache-Control} header to control other aspects of caching than
lifetime, i.e. to say that only private caches may use the response,
that the cache must be revalidated, or to prohibit caching.

@@

First, we compare dates given in \rdfterm{dct:modified} to dates given
in \httph{Last-Modified} when both are available for a resource. They
are often not the same, but it appears that dates in the former are
further back in time than the latter. We speculate that this may be
due to that the webserver tracks semantically insignificant changes
through the filesystem, while authors of RDF only update timestamp
when significant changes are made, or it may be that authors forget to
update their timestamps.

@@

\rdfterm{dct:valid} occurred 21 times, and could be used in lieu of an
\httph{Expires} header, but none of these occurences had a date in the
future.

@@

Hitherto, we have considered the case where the client or proxy does
not send a HTTP request to the server when a resource that is present
in the cache is requested. This is desireable if the client can be
sufficiently confident that the response is fresh, either by having a
standards-compliant freshness lifetime or a heuristic to determine
it. At the end of this period, or if the previous response had no
lifetime, due to lack of information, or to that the server has stated
so in the \httph{Cache-Control} header, responses must be
revalidated. In this case, RFC7232 defines the behaviour, with
\httph{ETag} and \httph{Last-Modified} as the relevant response
headers.

@@

\section{Future work}

@@

\section{Recommendations}\todo{write}

Based on the results of DyLDO, it is highly likely that most cache
prohibitions are misguided, and server administrators are adviced to
turn them off unless they are sure they are required.

>>>>

While these studies have little overlap with the present paper, they
underline the importance of understanding the current deployment and
future potential. In some of the related work, it is shown that
caching does not necessarily give tangible benefits. Yet, we shall
assume that sharing the meta data required for caching outside of the
server is desirable, and that it is possible in most cases. We shall
see that it most likely will be beneficial in cases that do not
benefit from caching today.

@@

The two most important headers to control caching are \httph{Expires}
and \httph{Cache-Control}. As shown in Table~\ref{tab:headers}, there
are also others. We found \httph{Pragma} in 287 responses, but except
for two hosts, where they were superfluous, they were only used to
prohibit caching. \httph{Surrogates} were not observed.

@@

Of these resources, 405 returned valid headers, but 114 did so to
\emph{prohibit} caching of the response, and 3 contained conflicting
headers, i.e. set an freshness lifetime, but also prohibited
caching. In most cases, \httph{Cache-Control} and \httph{Expires} both
occurred, but the former is more common than the latter in the cases
where only one of them occur.  Additionally, 269 resources had a
\httph{Cache-Control} header to control other aspects of caching than
lifetime, i.e. to say that only private caches may use the response,
that the cache must be revalidated, or to prohibit caching.

@@

First, we compare dates given in \rdfterm{dct:modified} to dates given
in \httph{Last-Modified} when both are available for a resource. They
are often not the same, but it appears that dates in the former are
further back in time than the latter. We speculate that this may be
due to that the web-server tracks semantically insignificant changes
through the file system, while authors of RDF only update timestamp
when significant changes are made, or it may be that authors forget to
update their timestamps.

@@

\rdfterm{dct:valid} occurred 21 times, and could be used in lieu of an
\httph{Expires} header, but none of these occurrences had a date in the
future.

@@

Hitherto, we have considered the case where the client or proxy does
not send a HTTP request to the server when a resource that is present
in the cache is requested. This is desirable if the client can be
sufficiently confident that the response is fresh, either by having a
standards-compliant freshness lifetime or a heuristic to determine
it. At the end of this period, or if the previous response had no
lifetime, due to lack of information, or to that the server has stated
so in the \httph{Cache-Control} header, responses must be
revalidated. In this case, RFC7232 defines the behaviour, with
\httph{ETag} and \httph{Last-Modified} as the relevant response
headers.

@@

\section{Conclusions and outlook}

We found that support for HTTP caching and conditional requests are
occurring regularly in the Semantic Web, but they are not
commonplace. We found, in agreement with DyLDO\cite{dyldo2}, that many
resources change at a very slow pace, but also that this is not
reflected in the standards-compliant freshness lifetimes advertized by
servers.

We found that errors are commonplace, but that they does not usually
pertain to the caching headers. We found a small number of
self-contradictory \httph{Cache-Control} headers, and some servers
that set conditional request response headers, that could not support
conditional requests.

It is possible in a substantial number of cases to compute a heuristic
freshness lifetime, either from the \httph{Last-Modified} header, or
from Dublin Core properties.

For SPARQL endpoints, we found that conditional requests are 
seldomly supported, but standards-compliant freshness lifetimes have
been seen, and since it is supported by DBPedia, benefits from caching
may be realized already.

In spite of this, most of the Semantic Web is unhelpful in spite of
being slowly changing.

\subsection{Future work}

@@

\subsection{Recommendations}\todo{write}

Based on the results of DyLDO, it is highly likely that most cache
prohibitions are misguided, and server administrators are advised to
turn them off unless they are sure they are required.
